Automated Synthesis of State-Space Digital Systems

### 2016-12-16 cav2017/cav2017.tex
benchmarks

The remaining of benchmarks represents classic DC-DC converters: buck, boost, and buck-boost. They are SISO second-order systems stable in open-loop, and their state vector is $\textbf{x}=\textbf{x}=\left[\begin{array}{c}
i_{L} \\ v_{C}\\
\end{array}\right]$, where $i_{L}$ is the current in the coil and $v_{c}$ is the voltage on the capacitor. The matrices $\textbf{A}$, $\textbf{B}$, $\textbf{C}$, and $\textbf{D}$ for the buck converter are:
$$
\textbf{A}=\left[\begin{array}{cc}
0		& -500 \\
4545	& -1515\\
\end{array}\right],~ \textbf{B} = \left[\begin{array}{c}
125 \\ 0 \\
\end{array}\right]~
\textbf{C}=\left[\begin{array}{cc}
0 & 1\\
\end{array}\right],~ \textbf{D}= 0.
$$

@@

>>>>

There are three benchmarks representing classic DC-DC converters: buck, boost, and buck-boost. They are SISO second-order systems stable in open-loop, and their state vector is $\textbf{x}=\textbf{x}=\left[\begin{array}{c}
i_{L} \\ v_{C}\\
\end{array}\right]$, where $i_{L}$ is the current in the coil and $v_{c}$ is the voltage on the capacitor. The matrices $\textbf{A}$, $\textbf{B}$, $\textbf{C}$, and $\textbf{D}$ for the buck converter are:
$$
\textbf{A}=\left[\begin{array}{cc}
0		& -500 \\
4545	& -1515\\
\end{array}\right],~ \textbf{B} = \left[\begin{array}{c}
125 \\ 0 \\
\end{array}\right]~
\textbf{C}=\left[\begin{array}{cc}
0 & 1\\
\end{array}\right],~ \textbf{D}= 0.
$$

@@

Additionally, various dynamic systems model were extracted from~\cite{Franklin15} and incorporated to our test suite. They are: 
\begin{itemize}
\item{\textbf{automotive cruise control system:} 
$$
\textbf{A}=-0.05,~ \textbf{B} = 0.03125~
\textbf{C}=0.032,~ \textbf{D}= 0;
$$
}
\item{\textbf{DC motor:} 
$$
\textbf{A}=\left[\begin{array}{cc}
-1000		& -13 \\
-8			& 0\\
\end{array}\right],~ \textbf{B} = \left[\begin{array}{c}
4 \\ 0 \\
\end{array}\right]~
\textbf{C}=\left[\begin{array}{cc}
0 & 6.25\\
\end{array}\right],~ \textbf{D}= 0;
$$
}
\item{\textbf{helicopter longitudinal motion:} 
$$
\textbf{A}=\left[\begin{array}{ccc}
-0.42		& 0.0168		& -0.396	\\
0.5			& 0				& 0			\\
0			& 0.5 			& 0			
\end{array}\right],~ \textbf{B} = \left[\begin{array}{c}
16 \\ 0 \\ 0
\end{array}\right]~
\textbf{C}=\left[\begin{array}{ccc}
0.6125	& -0.6125	& 15.44 \\
\end{array}\right],~ \textbf{D}= 0;
$$
}
\item{\textbf{inverted pendulum cart position:} 
$$
\textbf{A}=\left[\begin{array}{cccc}
0		& 1		& 0 	& 0	\\
1		& 0		& 0		& 0	\\
0		& 1 	& 0		& 0 \\
0		& 0		& 1 	& 0 \\	
\end{array}\right],~ \textbf{B} = \left[\begin{array}{c}
1 \\ 0 \\ 0 \\ 0
\end{array}\right]~
\textbf{C}=\left[\begin{array}{cccc}
0	& 0	& 1 & -0.75 \\
\end{array}\right],~ \textbf{D}= 0;
$$
}
\item{\textbf{inverted pendulum angle:} 
$$
\textbf{A}=\left[\begin{array}{cc}
0		& 1	\\
1		& 0	\\
\end{array}\right],~ \textbf{B} = \left[\begin{array}{c}
1 \\ 0 \\ 0 \\ 0
\end{array}\right]~
\textbf{C}=\left[\begin{array}{cc}
 0	& 1 \\
\end{array}\right],~ \textbf{D}= 0;
$$
}
\item{\textbf{magnetic pointer:} 
$$
\textbf{A}=\left[\begin{array}{ccc}
-0.271		& -0.05336	& 0	\\
0.03125		& 0			& 0	\\
0			& 0.01562 	& 0	\\	
\end{array}\right],~ \textbf{B} = \left[\begin{array}{c}
1 \\ 0 \\ 0
\end{array}\right]~
\textbf{C}=\left[\begin{array}{ccc}
0	& -0.5888	& -0.2562 \\
\end{array}\right],~ \textbf{D}= 0;
$$
}
\item{\textbf{magnetic suspension:} 
$$
\textbf{A}=\left[\begin{array}{cc}
0		& 31.25	\\
32		& 0		\\	
\end{array}\right],~ \textbf{B} = \left[\begin{array}{c}
8 \\ 0
\end{array}\right]~
\textbf{C}=\left[\begin{array}{cc}
0	& 9.766 	\\
\end{array}\right],~ \textbf{D}= 0;
$$
}
\item{\textbf{pendulum:} 
$$
\textbf{A}=\left[\begin{array}{cc}
0		& -2.453	\\
4		& 0			\\	
\end{array}\right],~ \textbf{B} = \left[\begin{array}{c}
4 \\ 0
\end{array}\right]~
\textbf{C}=\left[\begin{array}{cc}
-1.225	& -2.15 	\\
\end{array}\right],~ \textbf{D}= 9.8;
$$
}
\item{\textbf{1/4 car suspension:} 
$$
\textbf{A}=\left[\begin{array}{cccc}
-516.1	& -222.1& -79.75& -33.06	\\
256		& 0		& 0		& 0			\\
0		& 64 	& 0		& 0 \\
0		& 0		& 32 	& 0 \\	
\end{array}\right],~ \textbf{B} = \left[\begin{array}{c}
8 \\ 0 \\ 0 \\ 0
\end{array}\right]~
\textbf{C}=\left[\begin{array}{cccc}
0	& 0	& 9.969 & 4.133 \\
\end{array}\right],~ \textbf{D}= 0;
$$
}
\item{\textbf{computer tape driver:} 
$$
\textbf{A}=\left[\begin{array}{ccc}
-1760		& -976.6	& -457.8	\\
1024		& 0			& 0			\\
0			& 512 		& 0			\\	
\end{array}\right],~ \textbf{B} = \left[\begin{array}{c}
8 \\ 0 \\ 0
\end{array}\right]~
\textbf{C}=\left[\begin{array}{ccc}
1.5	& 2.051	& 1.144 \\
\end{array}\right],~ \textbf{D}= 0;
$$
}
\item{\textbf{USCG cutter Tampa heading angle:} 
$$
\textbf{A}=\left[\begin{array}{ccc}
-0.271		& -0.05336	& 0	\\
0.03125		& 0			& 0			\\
0			& 0.01562 	& 0			\\	
\end{array}\right],~ \textbf{B} = \left[\begin{array}{c}
1 \\ 0 \\ 0
\end{array}\right]~
\textbf{C}=\left[\begin{array}{ccc}
0	& -0.5888	& -0.2562 \\
\end{array}\right],~ \textbf{D}= 0;
$$
}
\end{itemize}
